cardinalR: Generating interesting high-dimensional data structures

### 2025-10-05 paper-cardinalR.Rmd
Updated Shape generator overview paragraph

The shape generators form the foundation of the package, providing a collection of functions to create synthetic data structures based on simple, well-defined geometric structures. These include fundamental shapes such as cones, pyramids, spheres, grids, and branching structures. If a shape is not inherently defined in more than two dimensions, additional noise dimensions can be added to embed the structure into higher-dimensional space. Users can specify how these noise dimensions are generated (e.g., Gaussian, wavy) (`noise_fun`), offering control over the embedding process. All shape generators allow the user to define the number of points (`n`), and most include additional arguments to customize specific characteristics of the structure.

>>>>

The shape generators form the foundation of the package, providing functions to create synthetic datasets from simple, well-defined geometric forms such as cones, pyramids, spheres, grids, and branching structures. Each generator includes the parameter `n`, which specifies the number of points to generate. Some functions, such as `gen_unifcube()`, also take the dimension `p`, while others include arguments specific to the geometry (e.g., radius for spheres (`r`), width for bands (`w`)). If higher-dimensional data are required, additional noise dimensions can be appended after data generation using any noise generator function. This flexibility allows users to construct both low- and high-dimensional datasets from the same underlying structures.

### 2025-10-05 paper-cardinalR.tex
Updated Shape generator overview paragraph

The shape generators form the foundation of the package, providing a collection of functions to create synthetic data structures based on simple, well-defined geometric structures. These include fundamental shapes such as cones, pyramids, spheres, grids, and branching structures. If a shape is not inherently defined in more than two dimensions, additional noise dimensions can be added to embed the structure into higher-dimensional space. Users can specify how these noise dimensions are generated (e.g., Gaussian, wavy) (\texttt{noise\_fun}), offering control over the embedding process. All shape generators allow the user to define the number of points (\texttt{n}), and most include additional arguments to customize specific characteristics of the structure.

>>>>

The shape generators form the foundation of the package, providing functions to create synthetic datasets from simple, well-defined geometric forms such as cones, pyramids, spheres, grids, and branching structures. Each generator includes the parameter \texttt{n}, which specifies the number of points to generate. Some functions, such as \texttt{gen\_unifcube()}, also take the dimension \texttt{p}, while others include arguments specific to the geometry (e.g., radius for spheres (\texttt{r}), width for bands (\texttt{w})). If higher-dimensional data are required, additional noise dimensions can be appended after data generation using any noise generator function. This flexibility allows users to construct both low- and high-dimensional datasets from the same underlying structures.
